---
title: "Trawind"
output: html_notebook
---
Following Wickham and Grolemund (2017), getting back to R

Short Cut Reminder: 

1) *Insert Chunk*: -> *Option+Cmd+=I*

2) *Preview* -> *Shift+Cmd+K*

3) *Running chunck* -> *Shift+Cmd+Enter*

4) *Clear Console* -> *Opt+ * 

Install packages recommended by Wickham and Grolemund (2017)
```{r}
install.packages("tidyverse", dependencies = TRUE)
versioninstall.packages("rlang", dependencies = TRUE)
install.packages(c("nycflights13", "gapminder", "Lahman"))
install.packages("chinese.misc", dependencies = TRUE)
install.packages("readxl", dependencies = TRUE)

```

Having the non-exit issue, trying this
```{r}
install.packages("tidyverse", repos = "http://cran.stat.ucla.edu/", dependencies = TRUE)
```





Reset the environment 
```{r}
rm(list=ls())
```

Now remind myself some of R's basic functions

First, load packages:
```{r}
library(rlang)
library(tidyverse)
library(chinese.misc)
library(readxl)
```

```{r}
mpg
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = hwy, color = class))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, shape = class, alpha = cyl))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) + facet_grid(drv ~ cyl)
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) + facet_grid(drv ~ .)
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
ggplot(data = mpg) + geom_smooth(mapping = aes(x = displ, y = hwy)) + geom_point(mapping = aes(x = displ, y = hwy))
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(color = class)) +
  geom_smooth(
    data = filter(mpg, class == "subcompact"),
    se = FALSE
  )
```

ggplot for bar charts

Now try something on the Trawind dataset

After cleaning the data, reload them into
```{r}
xinfeng_alf_cleaned <- read_excel("信风船价数据收集_cleaned.xlsx")
save(xinfeng_alf_cleaned, file = "Cleaned_Trawind_Data_V0.RData")

colnames(xinfeng_alf_cleaned)
colnames(xinfeng_alf_cleaned) <- c("dta_collection_time", "contract_time", "ship_time", 
                                   "bid_time", "vsl_company", "vsl_name", 
                                   "vsl_type", "customer", "total_weight", 
                                   "cargo_type", "start_port", "p", 
                                   "bid_port", "port_type", "port_type_value", 
                                   "port_price_diff", "distance", "customer_quote_time", 
                                   "actual_income", "actual_cost", "li_huo_cost", 
                                   "bang_dian_cost", "chao_qi_cost", "kau_gang_cost", 
                                   "same_time_competition", "other_factor", "NA"
                                   )
xinfeng_alf_cleaned_eng <- xinfeng_alf_cleaned
save(xinfeng_alf_cleaned_eng, file = "Cleaned_Trawind_Data_Eng_V0.RData")
```












